\section*{Acknowledgments} \label{acknowledgments}

Firstly I would like to thank Traverse Research for accommodating my research and providing incredible guidance. Secondly, I want to thank Jacco Bikker for inviting me to help organize High Performance Graphics 2023, and countless discussions about voxels, rendering and GPUs. Tertiary, I would like to thank Alex Telea for his very critical look at all the documents that I made during the past year and for always being able to help with any questions regarding my thesis, it was very helpful and taught me a lot. Fourthly, I want to thank Emilio Laiso for all the collaboration on the implementation side, and for integrating our two systems to allow for (in my opinion) very pretty renders. Furthermore, I would like to thank Manon Oomen for her support during my thesis and the nitty-gritty detailed explanations of GPU performance. And of course, I want to thank Devon Dissel for always being there to cheer me up and dealing with my long days away from home.

I also want to thank some communities that have helped me through the process of writing this thesis either on an emotional or technical level. Namely, The Revenant Rebellion for providing some distractions when stress was high. The VoxelGameDev.com community for providing technical help and staying up to date with the latest developments in volume data structure research. The study association Sticky for providing a comfortable space near the University to study and work. And lastly the Utrecht Skate Parade for keeping me fit throughout it all.